%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
  {} % Role
  {NDN in mobile ad-hoc, delay-tolerant and challenging networks.} % Title
  {Ongoing} % Location
  {} % Date(s)
  {
    \vspace{-3mm}
    \begin{cvitems} % Description(s)
      \item {\textbf{Problem:} Identify existing IP-network limitations and improve network performance in mobile ad-hoc, delay-tolerant networks.}
      \item {\textbf{Primary solution:} Understanding effect of NDN-based Interest-Data exchange on network performance.}
      \item {\textit{Sub-solution-1:} RTT-based hop-by-hop neighbor update for fast reaction to network dynamics.}
      \item {\textit{Sub-solution-2:} Neighborhood measurement in long-delay networks.}
      \item {\textbf{Expected outcome:} High data retrieval rate at low latency under moderate to high mobility and high reliability in long-delay communication.}
      \item {\textbf{Publications:} One under review at IEEE Globecom 2020.}
      \item {Tools: ndnSIM (built on NS-3), C++}
    \end{cvitems}
  }
  {}

%---------------------------------------------------------
% \cventry
%   {Student developer (Tools: boostc++, Gerrit, Jenkins)} % Role
%   {NFD: Named-Data Forwarding Daemon} % Title
%   {2016 - } % Location
%   {} % Date(s)
%   {
%     \begin{cvitems} % Description(s)
%       \item {A network forwarder that evolves together with the NDN protocol (Site: \url{https://named-data.net/doc/NFD/current/}).}
%     \end{cvitems}
%   }
%   {}

%---------------------------------------------------------
\cventry
  {} % Conference
  {Network Coded Data Dissemination in RSU-based Vehicular Ad-hoc Networks (VANETs)} % Title
  {2014-2019} % Location
  {} % Date(s)
  {
    \vspace{-3mm}
    \begin{cvitems} % Authors; comma separated
      \item {\textbf{Problem:} Minimize wireless broadcast data transmissions and overall Vehicle-to-RSU communication latency in VANETs to provide improved road-safety and infotainment.}
      \item {\textbf{Primary solution:} Network coded wireless broadcast with optimized scheduling algorithms for time sensitive data request}
      \item {\textit{Sub-solution-1}: Co-operative RSU-to-RSU cache information transfer which excludes explicit upload by vehicles.}
      \item {\textit{Sub-solution-2}: Coding for heterogeneous data with weighted moving average of maximum data size in a clique.}
      \item {\textit{Sub-solution-3}: Time-sensitive heuristic coding for heterogeneous data in real-time multi-item query.}
      \item {\textbf{Results}: Significant lower latency and wireless broadcast overhead with high data-retrieval rate.}
      \item {\textbf{Publications:} Two Journals and four Conference papers. Two as first author, two as second and two as third (\href{https://scholar.google.com/citations?user=hYY1wDEAAAAJ&hl=en}{\textcolor{cyan}{Google Scholar}}).}
      \item {Tools: CSIM}
    \end{cvitems}
  }
  {}

%---------------------------------------------------------
\cventry
    %{CSC 585 Algorithms in NLP} % Role
    {}
    {Weighted Dropout: Supporting Multi-Level Annotations for Medical Literature on Patient, Interventions and Outcomes} % Title
    {2018} % Location
    {}
    %{Fall 2018} % Date(s)
    {
      \vspace{-3mm}
      \begin{cvitems} % Description(s)
        \item {\textbf{Problem:} Annotating abstracts from medical literature.}
        \item {\textbf{Solution:} Variable-dropout based on distance from tokens of interest.}
        \item {Maintains higher context information from all hot-word neighbors.}
        \item {\textbf{Outcome:} Near-SotA performance with near-half model training time.}
        \item {\textit{Tools:} Python, Tensorflow, Docker.}
      \end{cvitems}
    }
    {}

%---------------------------------------------------------
  \cventry
    %{CSC 560 Database Systems and Implementations} % Conference
    {}
    {Components of MINIBASE DBMS in C} % Title
    {2017} % Location
    {}
    %{Fall 2017} % Date(s)
    {
      \vspace{-3mm}
      \begin{cvitems} % Authors; comma separated
        \item {Implemented self-resizing Heapfile manager, Buffer manager}
        \item {Implemented B+ tree (non-balancing)}
      \end{cvitems}
    }
    {}

%---------------------------------------------------------
  \cventry
    %{CSC 583 Text Retrieval \& Web Search} % Role
    {}
    {Building (a part of) Watson} % Title
    {2017} % Location
    {}
    %{Spring 2017} % Date(s)
    {
      \vspace{-3mm}
      \begin{cvitems} % Description(s)
        \item {An end-to-end Information Retrieval system that indexes a large set of Wikipedia pages to retrieve top relevant pages for short queries similar to the Jeopardy game.}
        \item {Tools: Scala, Apache Maven, Lucene.}
        %\item {Tools: Scala, Apache Maven, Lucene}
      \end{cvitems}
    }
    {}

%---------------------------------------------------------
  \cventry
    %{CSC 583 Text Retrieval \& Web Search} % Role
    {}
    {Email Spam classifier} % Title
    {2017} % Location
    {}
    %{Spring 2017} % Date(s)
    {
      \vspace{-3mm}
      \begin{cvitems} % Description(s)
        \item {Built a spam classifier model by training with spam labeled/unlabeled dataset and finding similarity between unknown dataset}
        \item {Tools: Scala, Apache Maven, Lucene.}
        %\item {Tools: Scala, Apache Maven, Lucene}
      \end{cvitems}
    }
    {}

%---------------------------------------------------------
  \cventry
    %{CSC 525 Principles of Computer Networking} % Conference
    {}
    {Implementing a Software Router in C} % Title
    {2016} % Location
    {}
    %{Fall 2016} % Date(s)
    {
      \vspace{-3mm}
      \begin{cvitems} % Authors; comma separated
        \item {\textit{Problem:} forward IP packets under possible link changes.}
        \item {\textit{Solution:} Wrote the ARP protocol, IP forwarding, and PWOSPF routing algorithm that can react to link changes.}
        %\item {Tools: C}
      \end{cvitems}
    }
    {}

%---------------------------------------------------------
  \cventry
    {} % Conference
    {Gas Station Automation} % Title
    {2014} % Location
    {} % Date(s)
    {
      \vspace{-3mm}
      \begin{cvitems} % Authors; comma separated
        \item {Easy and secured management of gas station's monetary, repository, and human resources and report generation using cloud services.}
        \item {Tools: C\#, SQL, ASP.NET, Crystal Report, JavaScript}
      \end{cvitems}
    }
    {}

%---------------------------------------------------------
\end{cventries}
