%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Publications (Undergraduate research)}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  \cventry
    {ACM Transaction on Embedded Computing Systems} % Conference
    {Cooperative Cache Transfer-based On-demand Network Coded Broadcast in Vehicular Networks} % Title
    {ACM} % Location
    {2019} % Date(s)
    {
      \begin{cvitems} % Authors; comma separated
        \item {G. G. MD. Nawaz Ali; MD. Noor-A-Rahim; Md. Ashiqur Rahman; Beshah Ayalew; Peter H. J. Chong; Yong Liang Guan}
      \end{cvitems}
    }
    {}

%---------------------------------------------------------
  \cventry
    {IEEE Internet of Things Journal} % Conference
    {Efficient Real-time Coding-assisted Heterogeneous Data Access in Vehicular Network} % Title
    {IEEE} % Location
    {2018} % Date(s)
    {
      \begin{cvitems} % Authors; comma separated
        \item {G. G. Md. Nawaz Ali; Md. Noor-A-Rahim; Md. Ashiqur Rahman; Syeda Khairunnesa Samantha; Peter Han Joo Chong; Yong Liang Guan}
      \end{cvitems}
    }
    {}

%---------------------------------------------------------
  \cventry
    {IEEE International Conference on Communications (ICC)} % Role
    {Efficient coding based heterogeneous data access in vehicular networks} % Title
    {France} % Location
    {2017} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {G. G. M. Nawaz Ali; Md. A. Rahman; S. K. Samantha; Yumeng Gao; Peter H.J. Chong; Y. L. Guan}
      \end{cvitems}
    }
    {}

%---------------------------------------------------------
  \cventry
    {IEEE 84th Vehicular Technology Conference (VTC-Fall)} % Conference
    {On Accessing Heterogeneous Data Items Using Network Coding in Wireless Broadcast} % Title
    {Canada} % Location
    {2016} % Date(s)
    {
      \begin{cvitems} % Authors; comma separated
        \item {Md. Ashiqur Rahman; G. G. Md. Nawaz Ali; Yumeng Gao; Syeda K. Samantha; Peter H. J. Chong}
      \end{cvitems}
    }
    {}

%---------------------------------------------------------
  \cventry
    {22nd IEEE RTCSA} % Conference
    {On Scheduling Real-Time Multi-item Query with Network Coding in Multi-RSU VANETs} % Title
    {S. Korea} % Location
    {2016} % Date(s)
    {
      \begin{cvitems} % Authors; comma separated
        \item {Md. A. Rahman; G.G.M. Nawaz Ali; Peter H.J. Chong; S.K. Samantha; M.F. Muntasir; C. Chen}
      \end{cvitems}
    }
    {}

%---------------------------------------------------------
  \cventry
    {IEEE 83rd Vehicular Technology Conference (VTC Spring)} % Conference
    {On Efficient Data Dissemination Using Network Coding in Multi-RSU VANETs} % Title
    {China} % Location
    {2016} % Date(s)
    {
      \begin{cvitems} % Authors; comma separated
        \item {G. G. Md. Nawaz Ali; Md. Ashiqur Rahman; Peter Han Joo Chong; Syeda Khairunnesa Samantha}
      \end{cvitems}
    }
    {}

%---------------------------------------------------------
\end{cventries}
